Evaluating Modern vs. Older Buildings: Detailed Analysis on the Apartment Building Evaluation 2023

### 2024-01-25 Output/Paper/BuildingScoreAnalyze-2023.qmd
Update on TA's suggestion

## Main Columns (Year, Score)

@@

## Secondary Columns (Decade and Average_score)

@@

## Other columns

@@

## Frequency of Full score on category in 1950 and 2000

@@

## Built year vs. Score

@@

## Percentage vs. Category

@@

```{r, fig.height=3, fig.width=5, fig.align='center'}
#| message: false
#| echo: false
#| label: fig-fig3
#| fig-cap: Comparing Each Category with the Percentage of a Building in its Decade of Achieveing Full Mark

## create a bar chart of evaluation standard vs. percentage with help of Chatgpt
ggplot(data_frequency, aes(x = Category, y = Value, fill = as.factor(Year))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_brewer(palette = "Set1") + 
  labs(x = "Category", y = "Percentage", title = "Percentage for buildings of achieving a full Mark") +
  scale_fill_manual(values = c("1950" = "pink", "2000" = "blue")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Unit number, Storey number vs. Score

>>>>

## Year and Score

@@

## Decade and Average_score

@@

## Address, Storeys, Units and Criterion for different Category

@@

## Frequency of full score on different category in 1950 and 2000

@@

@@

@@

```{r, fig.height=3, fig.width=5, fig.align='center'}
#| message: false
#| echo: false
#| label: fig-fig3
#| fig-cap: Probabilty for a building in different decade to achieve a full Mark in different category

## create a bar chart of evaluation standard vs. percentage with help of Chatgpt
ggplot(data_frequency, aes(x = Category, y = Value, fill = as.factor(Year))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_brewer(palette = "Set1") + 
  labs(x = "Category", y = "Probabilty", title = "Probabilty for a building to achieve a full Mark") +
  scale_fill_manual(values = c("1950" = "pink", "2000" = "blue")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
